\chapter{Introduction}
\epigraphhead[50]{
      \epigraph{\large{`There is another world, but it is in this one.'}}{Commonly attrib. Paul Éluard}
}


The topic of creating artificial life has been subject to fervent debate for
hundreds of years, but at the advent of modern computing this conversation took
a turn towards the technological. In his 2005 book “The Singularity Is Near:
When Humans Transcend Biology” author Ray Kurzweil predicts that rather than
creating new species that mimic humanity, we will be able to transfer our
consciousness to emulations of the human brain with far greater cognitive power
than our biological limits allow \autocite{kurzweil_singularity_2006}.

\begin{quote}
      `The Singularity will allow us to transcend [the] limitations of our
      biological bodies and brains. We will gain power over our fates. Our
      mortality will be in our own hands [\ldots] Although the Singularity has
      many faces, its most important implication is this: our technology will
      match and then vastly exceed the refinement and suppleness of what we
      regard as the best of human traits.'
\begin{flushright}
      \textit{-- Ray Kurzweil \\ The Singularity Is Near: When Humans Transcend
      Biology (\citeyear{kurzweil_singularity_2006})}
  \end{flushright}
\end{quote}  

The implication of this could be that, assuming inexhaustible power and
processing to maintain the simulation, humanity would be made immortal. However,
there are a number of constraints technologically that must be reckoned with
before this could even be attempted \parencite{bostrom_whole_2008}, alongside
the moral quandaries that are ever present when discussing the evolution and
modification of what it means to be human.

When discussing brain emulation, we envisage the “uploading” of consciousness,
which in basic terms is the measurement of electrical activity and neural
connections of a brain, and in theory would retain every mental process, keeping
them intact. Using current known techniques, this imaging and measurement
process would introduce error in numerous ways, herein referred to as
"measurement error"; it is perhaps possible that the resolution of the scanning
equipment is not large enough to capture the distances between neurons
correctly, or that changes in the network will occur while measurements are
taken. It is therefore unclear what impact this measurement error would have on
a simulation of the human brain.

In investigating the effect of measurement error on predicting brain activity in
a computational model, this dissertation aims to provide a link between the
theoretical measurement error in transferring the human mind to a simulation,
and the resulting accuracy of the simulation. This will be achieved through
comparison between a control simulation with no emulated measurement error and a
simulation with measurement error. 

\section{Motivation}

This project aims to investigate the effect of measurement error on the accuracy
of a brain simulation with and without synaptic plasticity, and to assess the
feasibility of predicting future brain activity, given the performance of
current imaging techniques.

The primary outcome of this project will be to provide tooling written in Python
that is capable of running concurrent simulations in a efficient manner, that can be modified during runtime to model the effect of measurement
error when `uploading' a brain into a simulation.

\section{Aims and objectives}

This project was originally planned to be built on top of the VERTEX simulator.
However, once my research began I decided that I would instead shift more
towards building the simulation tooling myself to learn and understand better
the mathematics that underpin computational neuroscience.

\subsubsection{Analyse and compare three published neural simulation packages.}

Developing an understanding of simulation packages and the models that they
implement will help me inform my design decisions for my own implementation of
this feature. This objective will have been completed when I have summarised and
understood the aims and features of three existing packages.


\subsubsection{Identify the experiments that should be performed to determine
      the relation between measurement error in data from imaging a brain, and the
      performance of a neural simulation of such data.}

In order to prove that measurement error has an effect on predicting future brain activity, I will
define experiments that can be performed within the limits of this project. Each
experiment must contribute either to the argument that measurement error has a
major negative impact on the accuracy of a neural simulation, or that
introducing plasticity into the simulation minimises this effect over time.


\subsubsection{Identify the requirements and features that the simulation
      tooling should implement to be capable of performing the project experiments.}

Given the experiments that are defined in order to meet the previous objective,
a set of requirements for the simulation software can be identified. This will
include the Python API presented to the user of the software, required data
structures to store information, and choosing functionality which forms the
minimal viable product. To achieve this, I will have collected enough research
to make conclusive design and functionality decisions.


\subsubsection{Identify
      the parameters in a brain simulation that can be modified during the simulation
      to emulate the measurement error of uploading the human brain.}

Many of the parameters required in the creation of a simulation, such as the
number of layers or the positions and links between neurons could be modified
during a simulation using the tooling this project aims to develop. To achieve
this objective I will identify these parameters, and justify why they have been
chosen over other parameters.


\subsubsection{Analyse the performance of simulations
      that diverge with different measurement errors from a starting simulation.}

This final objective will assess whether the software designed and developed
during the course of the project can correctly demonstrate the effect of
measurement error on brain simulation. This objective will be met once the
experiments are shown to provide reliable results.

% \begin{itemize} \item \textbf{Analyse and compare three published neural
%     simulation packages.}

%     \item \textbf{Identify the experiments that should be performed to
%               determine the relation between measurement error in data from
%               imaging a brain, and the performance of a neural simulation of
%               such data.}

%     \item \textbf{Identify the requirements and features that the simulation
%               tooling should implement to be capable of performing the project
%               experiments.} \item \textbf{Identify the parameters in a brain
%               simulation that can be modified during the simulation to emulate
%               the measurement error of uploading the human brain.} \item
%               \textbf{Analyse the performance of simulations that diverge with
%               different measurement errors from a starting simulation.}
%               \end{itemize}

% \section{Experiments and Hypotheses}
%

\section{Document structure}

\subsection*{Chapter 2: Background and Literature Review}
This chapter aims to evaluate the general position of what is considered
mainstream academic and industry opinion, and some of the more topical
approaches in each of the domains that this project touches on.

\subsection*{Chapter 3: Planning and Development}
This chapter will discuss the methodology by which project deliverables have
been developed, and explain the rationale of certain design decisions. In
particular, functionality of the neural network simulation will be discussed, as
will the simulation parameters.

\subsection*{Chapter 4: Results, Analysis and Evaluation}
The underpinning reliability of the Python simulation is verified here, and each
of the experiments that form the basis of the arguments made in this
dissertation are expanded on and the project results are explained.

An analysis and evaluation will review the results in the previous chapter and
show how the results reflect on the overall project aims. The results of all the
experiments are reviewed holistically and compared with expected findings.

\subsection*{Chapter 5: Ethical Considerations for Brain Simulation}
This chapter will offer an analysis of some moral and ethical consequences of
brain simulation, and in particular, the possible consequences of an imperfect
copying of the human mind to a simulation.

\subsection*{Chapter 6: Conclusion}
This chapter will offer a summary of the project, and whether the aim and
objectives have been met. This project is evaluated against its aims and
objectives. Future work that could be completed in another project will be
identified.